---
title: "Car Speed Presentation"
author: "Vasco Pereira"
date: "9/15/2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, include = FALSE, message = FALSE)
```

## Abstract

Drivers that circulate inside cities in Portugal have a maximum speed limit of 50 km/h, but the behaviour is not always in compliance with the law.
After observing the possibility of high speeds in the road *Avenida Almirante Gago Coutinho* in *Mem-Martins*, *Sintra*, *Portugal*, the vehicle speed was measured with a **Raspberry Pi Zero W** and an exploratory data analysis was performed in **R**.
It was verified that the vehicles moving from *Mem-Martins* to *Sintra* had a mean speed of **69 km/h** and from *Sintra* to *Mem-Martins* had a mean speed of **87 km/h**
This road have a pedestrian crossing about 40 meters after the experimental measuring local, and two schools and a sports hall nearby that encourage the presence of many pedestrians in the sidewalk of this road.

**About**

To know more about this project in the original repo [carspeed](https://github.com/VascoRibeiroPereira/carspeed.py)

## Data

Data after cleaning:

```{r }

library(lubridate)
library(dplyr)

myData <- read.csv("cleanData.csv", 
                       colClasses = c("factor", "POSIXct", "factor", "numeric"))

myData <- as_tibble(myData)[,-1]

```

```{r, include=TRUE }

str(myData)

summary(myData)

```